Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-21 manuscript/manuscript.tex
Fixed wrong Neuquen Basing typing
Started fixing grids issue

We present a new algorithm for computing the gravitational fields generated by any
tesseroid with an arbitrary continuous density function on any external point.
It is based on the GLQ approximation and the adaptive discretization of
\citet{Uieda2016}, which we extend to include a new density-based discretization step.
In order to ensure the accuracy of the numerical approximation we have
determined optimal values for the controlling parameters by
comparing the numerical approximation with analytical solutions for
spherical shells.
Finally, we applied the methodology to model the Nequen basin, Argentina, using
tesseroids with an exponentially increasing density with depth.

@@

In order to compare the numerical results with the analytical solution we
must build a spherical shell made of tesseroids.
We use a combination of tesseroid models with different resolutions and compute their
effects on $10 \times 10$ point grids at different heights and locations.
All combinations of models and grids are shown in Table \ref{tab:grids}.
The tesseroid model is composed of a single radial layer.
The combinations in Table \ref{tab:grids} are repeated for two shells with thickness 1
km and 35 km.
The outer radius of both shells are equal to the mean Earth radius and
the density varies linearly (Eq. \ref{eq:density-linear})
with angular coefficient

>>>>

We present a new algorithm for computing the gravitational fields generated by any
tesseroid with an arbitrary continuous density function on any external point.
It is based on the GLQ approximation and the adaptive discretization of
\citet{Uieda2016}, which we extend to include a new density-based discretization step.
In order to ensure the accuracy of the numerical approximation we have
determined optimal values for the controlling parameters by
comparing the numerical approximation with analytical solutions for
spherical shells.
Finally, we applied the methodology to model the Neuqu\'en basin, Argentina, using
tesseroids with an exponentially increasing density with depth.

@@

In order to compare the numerical results with the analytical solution we
must build a spherical shell made of tesseroids.
We use a single radial layer of $30^\circ \times 30^\circ$ tesseroids to
build the spherical shell.
We compute their gravitational effects on $10 \times 10$ point grids at
different heights and locations.
These grids are defined in Table \ref{tab:grids}.
The computation of the gravitational effects on each grid is repeated for
two shells with thickness 1km and 35 km.
The outer radius of both shells are equal to the mean Earth radius and
the density varies linearly (Eq. \ref{eq:density-linear})
with angular coefficient
